Personalization and probabilities: impersonal propensities in online grocery shopping

### 2017-08-02 log.rmd
updating slides
18/32 pages revised
27/31 pages

## Mon 31 Jul 2017 11:47:42 BST
- printing as docx. There are around 35 pages on manuscript. Plan for revision: 7 pages/day for one week; (7 hours)  go through referee reports again alongside the manuscript to put them in (2 hours); redo diagrams and references (3 hours), submission (1 hour). Total of about 12 hours. Might be to do about 6-7 hours this week.

>>>>

## Mon 31 Jul 2017 11:47:42 BST
- printing as docx. There are around 35 pages on manuscript. Plan for revision: 7 pages/day for one week; (5 hours); enter edits 5 hours;  go through referee reports again alongside the manuscript to put them in (2 hours); redo diagrams and references (3 hours), submission (1 hour). Total of about 16 hours. Might be to do about 6-7 hours this week.     
- did 8 pages of revisions; and 20 edits

## Tue 01 Aug 2017 15:53:17 BST
- did another 10 pages of revisions -- up to 51 edits

## Wed 02 Aug 2017 10:49:46 BST
- reached page 27/31 in edits  on paper
